Multilocus Genotype And Mycelial Compatability Group Assessment

### 2017-09-07 doc/RMD/mlg-mcg.Rmd
remove labels from nodes where n = 1

```{r top5graph, fig.height = 7, fig.width = 7}
top5 <- filter(mcgmlg, as.character(MCG) %in% (mcgs %>% arrange(desc(Samples)) %>% slice(1:8) %>% pull(MCG)))
top5g <- make_mcgmlg_graph(top5)
tosize <- V(top5g)$size
V(top5g)$size <- sqrt(tosize)/10
# set.seed(2017-05-08)
set.seed(2017-08-1)
top5lay <- create_layout(top5g, layout = "igraph", algorithm = "fr", weights = rep(1, length(E(top5g))))
top5lay$community <- inner_join(data_frame(vertex = top5lay$name), the_communities)$comm
levels(top5lay$type) <- c("Multilocus Haplotype", "Mycelial Compatibility\nGroup")
t5g <- ggraph(top5lay) +
  geom_node_circle(aes(r = size, fill = type)) +
  geom_edge_link(aes(start_cap = circle(node1.size, unit = "native"), 
                     end_cap = circle(node2.size, unit = "native"), 
                     width = weight),
                 arrow = arrow(length = unit(0.01, "native"))) +
  geom_node_text(aes(label = gsub("MLG.", "", name), # ifelse(size > 0.1, gsub("MLG.", "", name), ""), 
                     color = type, 
                     size = size/10),
                 show.legend = FALSE) +
  coord_fixed() +
  scale_edge_width(range = c(0.25, 1.5)) +
  scale_fill_manual(values = c("black", "white")) +
  scale_color_manual(values = c("white", "black")) +
  theme_graph(base_size = 16, base_family = "Helvetica") +
  # theme(legend.position = c(0.85, 0.35), legend.direction = "vertical") +
  theme(legend.position = c(0.5, 0), legend.direction = "horizontal", legend.box = "horizontal") +
  theme(legend.box.spacing = unit(-1, "lines")) +
  theme(legend.spacing.x = unit(0, "lines")) +
  # theme(legend.box.background = element_rect(color = "black")) +
  theme(legend.text = element_text(size = 10)) +
  theme(plot.margin = unit(c(0, 0, 0, 0), "lines"))
t5g$labels$edge_width <- "Shared Isolates"
t5g$labels$fill <- ""
t5g

>>>>

```{r top5graph, fig.height = 7, fig.width = 7}
top5 <- filter(mcgmlg, as.character(MCG) %in% (mcgs %>% arrange(desc(Samples)) %>% slice(1:8) %>% pull(MCG)))
top5g <- make_mcgmlg_graph(top5)
tosize <- V(top5g)$size
V(top5g)$size <- sqrt(tosize)/10
# set.seed(2017-05-08)
set.seed(2017-08-1)
top5lay <- create_layout(top5g, layout = "igraph", algorithm = "fr", weights = rep(1, length(E(top5g))))
top5lay$community <- inner_join(data_frame(vertex = top5lay$name), the_communities)$comm
levels(top5lay$type) <- c("Multilocus Haplotype", "Mycelial Compatibility\nGroup")
t5g <- ggraph(top5lay) +
  geom_node_circle(aes(r = size, fill = type)) +
  geom_edge_link(aes(start_cap = circle(node1.size, unit = "native"), 
                     end_cap = circle(node2.size, unit = "native"), 
                     width = weight),
                 arrow = arrow(length = unit(0.01, "native"))) +
  geom_node_text(aes(label = ifelse(size > 0.1, gsub("MLG.", "", name), ""), 
                     color = type, 
                     size = size/10),
                 show.legend = FALSE) +
  coord_fixed() +
  scale_edge_width(range = c(0.25, 1.5)) +
  scale_fill_manual(values = c("black", "white")) +
  scale_color_manual(values = c("white", "black")) +
  theme_graph(base_size = 16, base_family = "Helvetica") +
  # theme(legend.position = c(0.85, 0.35), legend.direction = "vertical") +
  theme(legend.position = c(0.5, 0), legend.direction = "horizontal", legend.box = "horizontal") +
  theme(legend.box.spacing = unit(-1, "lines")) +
  theme(legend.spacing.x = unit(0, "lines")) +
  # theme(legend.box.background = element_rect(color = "black")) +
  theme(legend.text = element_text(size = 10)) +
  theme(plot.margin = unit(c(0, 0, 0, 0), "lines"))
t5g$labels$edge_width <- "Shared Isolates"
t5g$labels$fill <- ""
t5g
